Generality in food webs scales with species richness not not with latitude

### 2015-05-20 manuscript/latitudepaper.tex
Some DBS comments

\title{Generality in food webs scales with species richness, not latitude}
\author{Alyssa Cirtwill, Daniel Stouffer, Tamara Romanuk}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand}

>>>>

\title{Generality in food webs scales with species richness not not with latitude}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand}
\medskip$^2$Department of Biology\\Life Science Centre\\
Dalhousie University\\1355 Oxford St.\\P0 BOX 15000\\
Halifax, NS B3H 4R2\\Canada\\}
